Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs

### 2020-05-27 main.tex
Updates from Overleaf

\title{Robust-Adaptive Control of Linear Systems: beyond Quadratic Costs}

@@

\begin{abstract}
%We develop a framework for the robust adaptive model predictive control (MPC) of a linear system with unknown parameters, in a critical setting where failures are costly. So far, this problem has been studied in the case of quadratic costs --the LQ problem--, which limits applications to stabilisation tasks. In this paper, we extend this setting to consider arbitrary bounded costs, including non-convex, that arise in many practical problems. To this end, we carefully select and bring together several tools from different communities, namely linear regression, recent results in interval prediction, and tree-based planning. Thanks to the non-trivial combination of theoretical guarantees at each layer, we provide the first end-to-end regret analysis in this setting. Finally, we relax our modelling assumptions in a multi-model extension based on a data-driven robust model selection mechanism. In addition to our theoretical results we strived to preserve tractable computations for practical applicability, as we illustrate on a two simulated applications.
We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned on the way (adaptive), in a critical setting where failures are costly (robust).
This problem has been studied from different perspectives by different communities. However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks. In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems,
we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. 
Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.  
Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions.
Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
\end{abstract}

>>>>

\title{Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs}

@@

\begin{abstract}
We consider the problem of robust and adaptive model predictive control (MPC) of a linear system, with unknown parameters that are learned on the way (adaptive), in a critical setting where failures are costly (robust).
This problem has been studied from different perspectives by different communities. However, only the case of quadratic costs --the LQ problem-- has been considered, which limits applications to stabilisation tasks only. In order to handle more general (bounded, non-convex) costs that naturally arise in many practical problems,
we carefully select and bring together several tools from different communities, namely non-asymptotic linear regression, recent results in interval prediction, and tree-based planning. 
Combining and adapting the theoretical guarantees at each layer is non trivial, and we provide the first end-to-end regret analysis for this setting.  
Interestingly, our analysis naturally adapts to handle many models and combines with a data-driven robust model selection strategy, which enables to relax the modelling assumptions.
Last, we strive to preserve tractability at any stage of the method, that we illustrate on two challenging simulated environments.\footnote{Source code and videos are available in the Supplementary Material.}
\end{abstract}
